% resume.tex
% position: software engineer

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
% \usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Derek Qian}}

1245 SW Grover St\ \ \textbullet
\ \ Apt\ 303\ \ \textbullet
\ \ Portland, OR 97239
\\
(503) 267-5036\ \ \textbullet
\ \ derek.dejun@gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Portland State University}}
		{\textbf{Portland, OR}}
	\\
	\headerrow
		{\emph{Student \& Teaching Assistant}}
		{\emph{2011 -- present}}
	\begin{itemize*}
		\item Research Project: coDoc, a tool managing code and its spec. (Eclipse, Java,
                C++, JNI, SWT, RCP, CDT, poppler, Cario)
		\item Course Project: CrazyPuzzle, a math puzzle game for Android platform. (Eclipse, Java, Android)
		\item Course Project: Arum, a lightweight, easy-to-use, all-in-one solution
                for colleting a variety of performance data of applications. (Dyninst, C/C++, Linux, GNU Make, \LaTeX)
		\item Course Project: ftpread, a simple ftp client working in both passive
                and active mode. (FTP, TCP/IP, C, socket)
		\item Course Project: projects from parallel programing course. (Linux, pthread, OpenMP, MPI, python)
		\item Teach Assistant: Data Structures, Computer Systems Programming,
		Discrete Structures, Elements Of Software Engineering.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Skypine Co., Ltd.}}
		{\textbf{www.skypine.cn}}
	\\
	\headerrow
		{\emph{Senior Software Engineer}}
		{\emph{2011 -- 2011}}
	\begin{itemize*}
		\item The core board for Navigation Unit using i.MX51 processor and Windows CE 6.0/Android 2.3. (Visual Studio,
                BSP, Bootloader, Kernel, Driver, Embedded Linux, Android Framework)
		\item Optimized the media player. (Direct Draw, Direct Show, Overlay, YUV, RGB)
		\item Customized the touchscreen calibrator.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Seuic, LLC.}}
		{\textbf{www.seuic.com}}
	\\
	\headerrow
		{\emph{Senior Software Engineer \& Project Manager}}
		{\emph{2004 -- 2010}}
	\begin{itemize*}
		\item Managed the project developing a smartphone using PXA310 processor
                and Windows CE6.0. (XSCALE, OAL, MS Project, WTL, MFC)
		\item Smartphone using PXA270 and Windows Mobile 6.04.
		\item PND (Portable Navigation Device), using PXA 270 and Windows CE 4.2. (NMEA, MLC NAND flash, FMD, FAL, ECC)
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Portland State University}}
		{\textbf{Portland, OR}}
	\\
	\headerrow
		{\emph{College of Engineering \& Computer Science, M.S. Computer Science}}
		{\emph{2011 -- present}}
	\begin{itemize*}
		\item GPA 3.91/4.0.
	\end{itemize*}

	\item 
	\headerrow
		{\textbf{Southeast University}}
		{\textbf{Nanjing, Jiangsu, China}}
	\\
	\headerrow
		{\emph{PhD candidate, Electrical and Electronics Engineering}}
		{\emph{2008 -- 2011}}
	\begin{itemize*}
		\item GPA 3.67/4.0.
	\end{itemize*}

	\item 
	\headerrow
		{\textbf{Southeast University}}
		{\textbf{Nanjing, Jiangsu, China}}
	\\
	\headerrow
		{\emph{M.S. Electrical and Electronics Engineering}}
		{\emph{2004 -- 2007}}
	\begin{itemize*}
		\item Top 10\%.
	\end{itemize*}

	\item 
	\headerrow
		{\textbf{Southeast University}}
		{\textbf{Nanjing, Jiangsu, China}}
	\\
	\headerrow
		{\emph{Bachelor's degree, Electrical and Electronics Engineering}}
		{\emph{2000 -- 2004}}
	\begin{itemize*}
		\item Top 10\%.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
	C, \CPP, Java, x86/ARM assembly, \LaTeX, Python, shell script, SQL, makefile
	\item[Tools:]
	Visual Studio, Platform Builder, Eclipse, emacs/vim, git/svn, PADS
\end{description*}
\end{indentsection}

\end{document}
