% resume.tex
% position: embedded system engineer

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
% \usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Derek Qian}}

1245 SW Grover St\ \ \textbullet
\ \ Apt\ 303\ \ \textbullet
\ \ Portland, OR 97239
\\
(503) 267-5036\ \ \textbullet
\ \ derek.dejun@gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
	C, \CPP, Java, x86/ARM assembly, makefile, shell script, Python, SQL, \LaTeX
	\item[Tools:]
	gcc, arm-gcc, emacs/vim, git/svn, Visual Studio, Platform Builder, Eclipse, PADS
	\item[Open source projects:]
	Android, linux kernel, u-boot, busybox, buildroot, poppler
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Portland State University}}
		{\textbf{Portland, OR}}
	\\
	\headerrow
		{\emph{College of Engineering \& Computer Science, M.S. Computer Science}}
		{\emph{2011 -- present}}
	\begin{itemize*}
		\item GPA 3.91/4.0.
	\end{itemize*}

	\item 
	\headerrow
		{\textbf{Southeast University}}
		{\textbf{Nanjing, Jiangsu, China}}
	\\
	\headerrow
		{\emph{PhD candidate, Electrical and Electronics Engineering}}
		{\emph{2008 -- 2011}}
	\begin{itemize*}
		\item GPA 3.67/4.0.
	\end{itemize*}

	\item 
	\headerrow
		{\textbf{Southeast University}}
		{\textbf{Nanjing, Jiangsu, China}}
	\\
	\headerrow
		{\emph{M.S. Electrical and Electronics Engineering}}
		{\emph{2004 -- 2007}}
	\begin{itemize*}
		\item Top 10\%.
	\end{itemize*}

	\item 
	\headerrow
		{\textbf{Southeast University}}
		{\textbf{Nanjing, Jiangsu, China}}
	\\
	\headerrow
		{\emph{Bachelor's degree, Electrical and Electronics Engineering}}
		{\emph{2000 -- 2004}}
	\begin{itemize*}
		\item Top 10\%.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Portland State University}}
		{\textbf{Portland, OR}}
	\\
	\headerrow
		{\emph{Student \& Teaching Assistant}}
		{\emph{2011 -- present}}
	\begin{itemize*}
		\item Course Project: CrazyPuzzle, a math puzzle game for Android platform. (Eclipse, Java, Android)
		\item Course Project: ftpread, a simple ftp client working in both passive
                and active mode. (FTP, TCP/IP, C, socket)
		\item Course Project: projects from parallel programing course. (Linux, pthread, OpenMP, MPI, python)
		\item Course Project: Arum, a lightweight, easy-to-use, all-in-one solution
                for colleting a variety of performance data of applications. (Dyninst, C/C++, Linux, GNU Make, \LaTeX)
		% \item Research Project: coDoc, a tool managing code and its spec. (Eclipse, Java,
                % C++, JNI, SWT, RCP, CDT, poppler, Cario)
		\item Teach Assistant: Data Structures, Computer Systems Programming,
		Discrete Structures, Elements Of Software Engineering.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Skypine Co., Ltd.}}
		{\textbf{www.skypine.cn}}
	\\
	\headerrow
		{\emph{Senior Software Engineer}}
		{\emph{2011 -- 2011}}
	\begin{itemize*}
		\item The core board for Navigation Unit using i.MX51 processor and Android 2.3. (u-boot, Embedded Linux, 
                Android Framework, Driver)
		\item The core board for Navigation Unit using i.MX51 processor and Windows CE 6.0. (Visual Studio, BSP, 
                Bootloader, Kernel, Driver)
		\item Optimized the media player. (Direct Draw, Direct Show, Overlay, YUV, RGB)
		\item Customized the touchscreen calibrator.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Seuic, LLC.}}
		{\textbf{www.seuic.com}}
	\\
	\headerrow
		{\emph{Senior Software Engineer \& Project Manager}}
		{\emph{2004 -- 2010}}
	\begin{itemize*}
		\item PDA (Personal Digital Assistant), using PXA 255 and Embedded Linux. (u-boot, linux kernel, device driver)
		\item Managed the project developing a smartphone using PXA310 processor
                and Windows CE6.0. (XSCALE, OAL, MS Project, WTL, MFC)
		% \item Smartphone using PXA270 and Windows Mobile 6.04.
		\item PND (Portable Navigation Device), using PXA 270 and Windows CE 4.2. (NMEA, MLC NAND flash, FMD, FAL, ECC)
	\end{itemize*}

\end{itemize}


\end{document}
